The first high-redshift Changing Look Quasars

### 2019-11-07 tex/other_tex/201909/CIV_notes_20190923.tex
CIV tex/ tidy up

%\hypersetup{draft}
\begin{document}
\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle

@@

Samples of over 100 ``Changing Look'' quasars (CLQs) or ``Changing
State'' quasars (CSQs) have now been assembled
\citep[e.g.][]{MacLeod2019, Graham2019}. The community uses both these
terms as a cover for the underlying physics. For sake of argument,
``Changing Look'' quasars can be thought of as the extension of
``regular'' quasar variability \citep[e.g.][]{MacLeod2012} whereas the
``Changing State'' quasars (CSQs) have a `state-transition' similar to
that in Galactic X-ray binaries \citep[e.g][]{NodaDone2018, Ruan2019}.
These CLQs have primarily been defined according to the
(recombination) Balmer emission line properties with particular
attention paid to the H$\beta$ emission line, usually observed from
optical spectroscopy.  As such, current CLQ studies have been at
redshifts $z<1$.

@@

% &&\\
 \hline 
                                       &                                   &                        &             &                          &                   &                             &  & \\
   J120544.7+342252.4   & 2.068$\pm$0.0003   &   18.27            & 53498  &  2005-May-08  & SDSS             & ?                          & 53498-2089-427  & \\
          181.436164           & 2.071                        & {\bf 17.99??}  & 58538  &  2019-Feb-24   & DBSP            &  2$\times$900    &                               &  Conditions? \\
         +34.381229           &                                   &                          & 58693  &  2019-Jul-29    & DBSP            &  2$\times$1200   &                                &   \\
                                       &                                   &               &              &                           &                   &                             &  & \\
   J163852.9+282707.7   & 2.185$\pm$0.0004   &   19.77    & 54553 & 2008-Mar-28    & SDSS             & ?                          & 54553-2948-614  & \\
      249.720558407	       &  2.186$\pm$0.0007   &              & 55832  & 2011-Sep-28     & BOSS            &   3603                  & 55832-5201-178  & \\
       +28.452158884        &  2.182             &                & 58583 & 2019-Apr-10        & LRIS              &  2$\times$900    &   & \\
                                       &                                     &                   &              &                           &                   &                             &  & \\
    J222818.7+220102.9   & 2.217$\pm$0.0021    & 19.97      & 56189 & 2012-Sep-19     & BOSS             &  2702               & 56189-6118-720   & \\
        337.078194              & 2.222$\pm$0.0004    &                & 56960 & 2014-Oct-30    & BOSS             & ?                         & 56960-7582-790     & QSO1-REOBS \\ 
        +22.017478              &                                   &                & 58693 & 2019-Jul-29      & DBSP              & 2$\times$1200  &       &    \\
                                        &                                     &                &            &                            &                   &                              &  & \\
   \hline \hline   
  \end{tabular}
  \caption{Spectrum is SDSS/BOSS MJD-Plate-FiberID combination. 
Exposure times are from the {\tt plate.fits} file. 
DBSP on the Palomar 200-inch telescope is the } 
 \label{tab:obs_notes}
\end{table*}
\subsection{Spectra}
An overview of our spectroscopic observations is given in Table~\ref{tab:obs_notes}. 
The spectra are from the SDSS \citep{Stoughton2002, DR7, Schneider2010},  
the SDSS-III Baryon Oscillation Spectroscopic Survey \citep[BOSS][]{Eisenstein2011, Dawson2013, Smee2013, Alam2015, Paris2017} 
and the SDSS-IV  Extended Baryon Oscillation Spectroscopic Survey \citep[eBOSS; ][]{Dawson2016, Abolfathi2018}. 
These quasars were targetted via a range of techniques and algorithms \citep[][]{Richards2002, Ross2012, 
Myers2015}.  
These data are supplemented by spectra from 
the Low Resolution Imaging Spectrometer (LRIS) on the 10m Keck {\sc I} telescope \citep{Oke1995}. 
%% The Keck Low Resolution Imaging Spectrometer", Oke, J.B., et al.. 1995, PASP, 107, 375
and the Double Spectrograph (DBSP) instrument on the Palomar {\it Hale} 5m telescope.

\subsection{Line Properties}  
We use the measured quasar emission line properties from \citet{Shen2011} and \citet{Hamann2017}. \citet{Hamann2017} in particular investigate in robust detail the UV continuum and the \civ (and \nv $\lambda$ $\lambda$1238, 1242) emission lines in over 200,000 quasars in BOSS DR12Q \citep{Paris2017}\footnote{This emission-line catalog can be downloaded from \href{https://datadryad.org/stash/dataset/doi:10.6086/D1H59V}{here}.} The quasar redshift are limited to the range 1.53 ≤ ze ≤ 5.0 so that C IV and the adjacent continuum are covered by BOSS. These measurements provide line profile information and N V/C IV flux ratios... 
\input{Ham17_clqs}

>>>>

\hypersetup{draft}
\begin{document}
\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle

@@

The optical continuum variability of quasars has been recognized since
their first optical identification 
\citep[e.g.,][]{MatthewsSandage1963, MacLeod2012}.  However, dramatic
changes in the broad emission lines (BELs) in quasars has only
recently been identified \citep[e.g.][]{LaMassa2015}.  Samples of over
100 ``Changing Look'' quasars (CLQs) or ``Changing State'' quasars
(CSQs) have now been assembled \citep[e.g.][]{MacLeod2019,Graham2019}. 
The community uses both these terms as a cover for the
underlying physics. For sake of argument, ``Changing Look'' quasars
can potentially be thought of as the extension to the BELs of quasar
continuum variability \citep[e.g.][]{MacLeod2012} whereas the
``Changing State'' quasars (CSQs) have a `state-transition' similar to
that in Galactic X-ray binaries \citep[e.g][]{NodaDone2018,
Ruan2019}. In this paper, we use the term `Changing Look', as we are
currently agnostic to the underlying physical processes.

These CLQs have primarily been defined according to the
(recombination) Balmer emission line properties with particular
attention paid to the H$\beta$ emission line, usually observed from
optical spectroscopy.  As such, current CLQ studies have been at
redshifts $z<1$.

@@

% &&\\
 \hline 
                                       &                                   &                        &             &                          &                   &                             &  & \\
   J120544.7+342252.4   & 2.068$\pm$0.0003   &   18.27            & 53498  &  2005-May-08  & SDSS             & ?                          & 53498-2089-427  & \\
          181.436164           & 2.071                        & {\bf 17.99??}  & 58538  &  2019-Feb-24   & DBSP            &  2$\times$900    &                               &  Conditions? \\
         +34.381229           &                                   &                          & 58693  &  2019-Jul-29    & DBSP            &  2$\times$1200   &                                &   \\
                                       &                                   &               &              &                           &                   &                             &  & \\
   J163852.9+282707.7   & 2.185$\pm$0.0004   &   19.77    & 54553 & 2008-Mar-28    & SDSS             & ?                          & 54553-2948-614  & \\
      249.720558407	       &  2.186$\pm$0.0007   &              & 55832  & 2011-Sep-28     & BOSS            &   3603                  & 55832-5201-178  & \\
       +28.452158884        &  2.182             &                & 58583 & 2019-Apr-10        & LRIS              &  2$\times$900    &   & \\
                                       &                                     &                   &              &                           &                   &                             &  & \\
    J222818.7+220102.9   & 2.217$\pm$0.0021    & 19.97      & 56189 & 2012-Sep-19     & BOSS             &  2702               & 56189-6118-720   & \\
        337.078194              & 2.222$\pm$0.0004    &                & 56960 & 2014-Oct-30    & BOSS             & ?                         & 56960-7582-790     & QSO1-REOBS \\ 
        +22.017478              &                                   &                & 58693 & 2019-Jul-29      & DBSP              & 2$\times$1200  &       &    \\
                                        &                                     &                &            &                            &                   &                              &  & \\
   \hline \hline   
  \end{tabular}
  \caption{Spectrum is SDSS/BOSS MJD-Plate-FiberID combination. 
Exposure times are from the {\tt plate.fits} file. 
DBSP on the Palomar 200-inch telescope is the } 
 \label{tab:obs_notes}
\end{table*}
\subsection{Spectra}
An overview of our spectroscopic observations is given in Table~\ref{tab:obs_notes}. 
The spectra are from the SDSS \citep{Stoughton2002, DR7, Schneider2010},  
the SDSS-III Baryon Oscillation Spectroscopic Survey \citep[BOSS][]{Eisenstein2011, Dawson2013, Smee2013, Alam2015, Paris2017} 
and the SDSS-IV  Extended Baryon Oscillation Spectroscopic Survey \citep[eBOSS; ][]{Dawson2016, Abolfathi2018}. 
These quasars were targetted via a range of techniques and algorithms \citep[][]{Richards2002, Ross2012, 
Myers2015}.  
These data are supplemented by spectra from 
the Low Resolution Imaging Spectrometer (LRIS) on the 10m Keck {\sc I} telescope \citep{Oke1995}. 
and the Double Spectrograph (DBSP) instrument on the Palomar {\it Hale} 5m telescope.

\begin{table*}
\begin{tabular}{ l rrrr rrrr rrrr rrrr rrrr rr|}
\hline
\hline 
Object (MJD)               & $f$1450 & $\alpha_{\civ}$    & $\alpha_{\rm allc}$    & REW                       & cREW   &  wREW  & FWHM              & cFWHM  &  wFWHM  & $\sigma$     \\
\hline 
J1638+2827 (55832) & 1.4659    & -3.3547             & -4.026$\pm$0.452 & 42.76$\pm$1.96  & 26.72  & 16.03  & 5210$\pm$226 & 4651      & 13444    & 3702          \\
J2228+2201 (56189) & 0.5101    & -1.5931             & -0.657$\pm$0.004 & 42.18$\pm$5.59  &  6.42   & 35.76  & 2994$\pm$620 & 1458      &   7636    & 3002           \\
\hline
\end{tabular}
 \caption{
Spectrum is SDSS/BOSS MJD-Plate-FiberID combination. 
\noindent {\tt f1450} = flux in the uncorrected BOSS spectrum at 1450 \AA\ rest (10$^{-17}$ ergs s$^{-1}$ cm$^{-2}$ \AA$^{-1}$) used to anchor the power law continuum fits beneath \civ\ and \nv , e.g., $f_{\lambda} = f_{1450}\, (\lambda /1450{\rm \AA})^{\alpha}$.
\noindent {\tt $alpha_{\civ}$} = power law continuum slope ($f_{\lambda}\propto \lambda^{\alpha}$) measured from the BOSS spectrum on either side of \civ .
\noindent {\tt $alpha_{\rm allc}$} = power law continuum slope ($f_{\lambda}\propto \lambda^{\alpha}$) between 1350 \AA\ and 2200 \AA\ in the flux corrected BOSS spectrum, listed only for quasars wit $z_{\rm e} \le 3.4$ (with 1$\sigma$ uncertainty). 
\noindent {\tt REW} = \civ\ REW (\AA ) from the line profile fit (with 1$\sigma$ uncertainty). 
\noindent {\tt cREW} = \civ\ REW (\AA ) for the core Gaussian component.
\noindent {\tt wREW} = \civ\ REW (\AA ) for the wing Gaussian component.
\noindent {\tt FWHM} = \civ\ FWHM (km/s) from the line profile fit (with 1$\sigma$ uncertainty). 
\noindent {\tt fwhmc} = \civ\ FWHM (km/s) for the core Gaussian only.
\noindent {\tt fwhmw} = \civ\ FWHM (km/s) for the wing Gaussian only.
\noindent {\tt $\sigma$} = \civ\ velocity dispersion (km/s) measured from the profile fit \citep{Peterson2004}.
} 
 \label{tab:Ham17_lines}
\end{table*}

\subsection{Line Properties}  
We use the measured quasar emission line properties from \citet{Shen2011} and \citet{Hamann2017}. \citet{Hamann2017} in particular investigate in robust detail the UV continuum and the \civ (and \nv $\lambda$ $\lambda$1238, 1242) emission lines in over 200,000 quasars in BOSS DR12Q \citep{Paris2017}\footnote{This emission-line catalog can be downloaded from \href{https://datadryad.org/stash/dataset/doi:10.6086/D1H59V}{here}.} The quasar redshift are limited to the range 1.53 ≤ ze ≤ 5.0 so that C IV and the adjacent continuum are covered by BOSS. These measurements provide line profile information and N V/C IV flux ratios... 
%\input{Ham17_clqs}
